---
title: "Descriptive Analysis"
author: "Zayne Sember"
date: "10/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(grid)
library(ggthemes)
library(modelsummary)
library(kableExtra)
library(zoo)
```

# Official House Member Twitter Data

## Pre-pandemic 


## Pandemic (January 20 to November 28, 2020)

Prepping the data
```{r}
covid.national$date <- as.Date(covid.national$date)

official.house.pandemic.agg <- official.house.pandemic.tweet.count %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)
```


Tweet Time Series
```{r}
p1 <- ggplot(official.house.pandemic.agg, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="dodgerblue3") +
  ylab("Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 9,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Congressional Tweet Frequency and COVID-19 Indicators (Jan-Nov 2020)")


p2 <- ggplot(official.house.pandemic.agg, aes(x=date)) +
  geom_line(aes(y=national_incremental_cases), size=0.5, color="sienna3") +
  ylab("Incremental Cases") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
      axis.title.y = element_text(size = 9,
                                  margin = margin(r = 10)),
      axis.text.y=element_text(size=8),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())


p3 <- ggplot(official.house.pandemic.agg, aes(x=date)) +
  geom_line(aes(y=national_incremental_deaths), size=0.5, color="orangered4") +
  xlab("") +
  ylab("Incremental Deaths") +
  theme_bw() +
  theme(axis.text.x=element_text(angle=60,hjust=1),
        axis.title.y = element_text(size = 9,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8)) +
  scale_x_date(date_breaks="1 month", date_labels="%b") +

grid.newpage()
grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), ggplotGrob(p3), size="last"))
```

Prepping the Data
```{r}
ohpa.D <- official.house.pandemic.tweet.count %>%
  filter(party.code==100) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohpa.R <- official.house.pandemic.tweet.count %>%
  filter(party.code==200) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)
```
TOTAL TIME SERIES
```{r}
# p4 <- ggplot(official.house.pandemic.agg, aes(x=date)) +
#   geom_line(aes(y=num.tweets), size=0.5, color="purple4") +
#   ylab("Tweets") +
#   theme_bw() +
#   theme(axis.title.x=element_blank(),
#         axis.title.y = element_text(size = 9,
#                                     margin = margin(r = 10)),
#         axis.text.y=element_text(size=8),
#         axis.text.x=element_blank(),
#         axis.ticks.x=element_blank()) +
#   ggtitle("Congressional Tweet Frequency and COVID-19 Indicators (Jan-Nov 2020)")

p5 <- ggplot(ohpa.D, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="darkblue") +
  ylab("Democrat Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Congressional Tweet Frequency by Party and COVID-19 Indicators (Jan-Nov 2020)")

p6 <- ggplot(ohpa.R, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="darkred") +
  ylab("Republican Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

p7 <- ggplot(official.house.pandemic.agg, aes(x=date)) +
  geom_line(aes(y=national_incremental_cases), size=0.5, color="sienna3") +
  ylab("Incremental Cases") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
      axis.title.y = element_text(size = 7,
                                  margin = margin(r = 10)),
      axis.text.y=element_text(size=8),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())


p8 <- ggplot(official.house.pandemic.agg, aes(x=date)) +
  geom_line(aes(y=national_incremental_deaths), size=0.5, color="black") +
  xlab("") +
  ylab("Incremental Deaths") +
  theme_bw() +
  theme(axis.text.x=element_text(angle=60,hjust=1),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8)) +
  scale_x_date(date_breaks="1 month", date_labels="%b")

grid.newpage()
grid.draw(rbind(ggplotGrob(p5), ggplotGrob(p6),
                ggplotGrob(p7), ggplotGrob(p8),size="last"))
```
PREPPING THE DATA
```{r}
ohpa.total <- official.house.pandemic.tweet.count[,1:14] %>% 
  group_by(name) %>% 
  mutate(total.tweets=sum(num.tweets)) %>%
  select(-date,-num.tweets) %>% 
  distinct()
```

TOTAL TWEET DISTRIBUTIONS
```{r}
# RAW DISTRIBUTION
q.T <- ggplot(ohpa.total, aes(x=total.tweets)) +
  geom_histogram(fill="purple4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma) +
  ylim(c(0,50)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Total Tweets for 116th House (Jan-Nov 2020)") +
  theme(plot.title = element_text(size=10))

q.D <- ggplot(ohpa.total %>% filter(party.code==100), aes(x=total.tweets)) +
  geom_histogram(fill="blue4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  ggtitle("Democrats") +
  theme(plot.title = element_text(size=10))

q.R <- ggplot(ohpa.total %>% filter(party.code==200), aes(x=total.tweets)) +
  geom_histogram(fill="red4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2500)) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  xlab("Total Tweets") +
  ggtitle("Republicans") +
  theme(plot.title = element_text(size=10))

grid.newpage()
grid.draw(rbind(ggplotGrob(q.T), ggplotGrob(q.D),
                ggplotGrob(q.R), size="last"))

# LOGGED DISTRIBUTION
q.lT <- ggplot(ohpa.total, aes(x=log(total.tweets))) +
  geom_histogram(fill="purple4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Logged Total Tweets by 116th House (Jan-Nov 2020)") +
  theme(plot.title = element_text(size=10))

q.lD <- ggplot(ohpa.total %>% filter(party.code==100), aes(x=log(total.tweets))) +
  geom_histogram(fill="blue4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  ylim(c(0,35)) +
  xlab("") +
  ylab("") +
  ggtitle("Democrats") +
  theme(plot.title = element_text(size=10))

q.lR <- ggplot(ohpa.total %>% filter(party.code==200), aes(x=log(total.tweets))) +
  geom_histogram(fill="red4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  ylim(c(0,35)) +
  ylab("") +
  xlab("Logged Total Tweets") +
  ggtitle("Republicans") +
  theme(plot.title = element_text(size=10))

grid.newpage()
grid.draw(rbind(ggplotGrob(q.lT), ggplotGrob(q.lD),
                ggplotGrob(q.lR), size="last"))

ohpa.total %>% arrange(desc(total.tweets)) %>% select(name, state.abb, district, party.code, total.tweets)
```
Party and Age
```{r}
#recode party code to be a dummy
ohpa.total <- ohpa.total %>% filter(party.code!=328) %>% mutate(party = recode(party.code, `100`=1, `200`=0))

ggplot(ohpa.total, aes(x=year.born, y=total.tweets)) +
  geom_point() +
  geom_smooth(method="lm") +
  ggtitle("Tweet Frequency and Age for the 116th House (Jan-Mar 2020)") +
  theme_bw()

ggplot(ohpa.total, aes(x=year.born, y=log(total.tweets))) +
  geom_point() +
  geom_smooth(method="lm") +
  ggtitle("Tweet Frequency and Age for the 116th House (Jan-Mar 2020)") +
  theme_bw()

# UNLOGGED REGRESSIONS
# Testing party and age
tweets_on_years <- lm(total.tweets ~ year.born, data=ohpa.total)
tweets_on_years_res <-resid(tweets_on_years)
ggplot(ohpa.total, aes(x=total.tweets,y=tweets_on_years_res)) +
  geom_point()
tweets_on_party <- lm(total.tweets ~ party, data=ohpa.total)
tweets_on_years_party <- lm(total.tweets ~ year.born + party, data=ohpa.total)
tweets_on_years_party_int <- lm(total.tweets ~ year.born*party, data=ohpa.total)
summary(tweets_on_years_party_int)

ms1 <- modelsummary(list(tweets_on_years, tweets_on_party, tweets_on_years_party, tweets_on_years_party_int), 
             stars=T,
             output="kableExtra")

save_kable(ms1, "Tables/tweets_on_age_party.png")

# Testing party and dwnom dim1
tweets_on_dim1 <- lm(total.tweets ~ dwnom.dim1, data=ohpa.total)
tweets_on_years_dim1 <- lm(total.tweets ~ year.born + dwnom.dim1, data=ohpa.total)
tweets_on_years_dim1_int <- lm(total.tweets ~ year.born*dwnom.dim1, data=ohpa.total)
summary(tweets_on_years_dim1_int)

ms2 <- modelsummary(list(tweets_on_years, tweets_on_dim1, tweets_on_years_dim1, tweets_on_years_dim1_int), 
             stars=T,
             output="kableExtra")

save_kable(ms2, "Tables/tweets_on_age_dim1.png")


# To log or not to log
qqnorm(resid(lm(log(total.tweets)~year.born, data=ohpa.total)))
qqline(resid(lm(log(total.tweets)~year.born, data=ohpa.total)))
qqnorm(tweets_on_years_res)
qqline(tweets_on_years_res)

```
```{r}
log_tweets_on_years <- lm(log(total.tweets) ~ year.born, data=ohpa.total)
log_tweets_on_party <- lm(log(total.tweets) ~ party, data=ohpa.total)
log_tweets_on_years_party <- lm(log(total.tweets) ~ year.born + party, data=ohpa.total)
log_tweets_on_years_party_int <- lm(log(total.tweets) ~ year.born*party, data=ohpa.total)

ms3 <- modelsummary(list(log_tweets_on_years, log_tweets_on_party, 
                         log_tweets_on_years_party,log_tweets_on_years_party_int), 
             stars=T,
             output="kableExtra")

save_kable(ms3, "Tables/log_tweets_on_age_party.png")

# Testing party and dwnom dim1
log_tweets_on_dim1 <- lm(log(total.tweets) ~ dwnom.dim1, data=ohpa.total)
log_tweets_on_years_dim1 <- lm(log(total.tweets) ~ year.born + dwnom.dim1, data=ohpa.total)
log_tweets_on_years_dim1_int <- lm(log(total.tweets) ~ year.born*dwnom.dim1, data=ohpa.total)


ms4 <- modelsummary(list(log_tweets_on_years, log_tweets_on_dim1,
                         log_tweets_on_years_dim1, log_tweets_on_years_dim1_int), 
             stars=T,
             output="kableExtra")

save_kable(ms4, "Tables/log_tweets_on_age_dim1.png")
```


## Prepandemic
Prepping the Data
```{r}
ohppa.D <- official.house.prepandemic.tweet.count %>%
  filter(party.code==100) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohppa.R <- official.house.prepandemic.tweet.count %>%
  filter(party.code==200) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohppa.total <- official.house.prepandemic.tweet.count[,1:14] %>% 
  group_by(name) %>% 
  mutate(total.tweets=sum(num.tweets)) %>%
  select(-date,-num.tweets) %>% 
  distinct()
```
TOTAL TIME SERIES
```{r}
r1 <- ggplot(official.house.prepandemic.agg, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="purple4") +
  ylab("Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 9,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Congressional Tweet Prepandemic Frequency (Jan 2019-Jan 2020)")

r2 <- ggplot(ohppa.D, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="darkblue") +
  ylab("Democrat Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

r3 <- ggplot(ohppa.R, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="darkred") +
  ylab("Republican Tweets") +
  xlab("") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(angle=60,hjust=1)) +
  scale_x_date(date_breaks="1 month", date_labels="%b") +

grid.newpage()
grid.draw(rbind(ggplotGrob(r1), ggplotGrob(r2),
                ggplotGrob(r3), size="last"))
```

TOTAL TWEET DISTRIBUTIONS
```{r}
# RAW DISTRIBUTION
t.T <- ggplot(ohppa.total, aes(x=total.tweets)) +
  geom_histogram(fill="purple4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2000)) +
  ylim(c(0,50)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Total Tweets for 116th House (Jan 2019-Jan 2020)") +
  theme(plot.title = element_text(size=10))

t.D <- ggplot(ohppa.total %>% filter(party.code==100), aes(x=total.tweets)) +
  geom_histogram(fill="blue4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2000)) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  ggtitle("Democrats") +
  theme(plot.title = element_text(size=10))

t.R <- ggplot(ohppa.total %>% filter(party.code==200), aes(x=total.tweets)) +
  geom_histogram(fill="red4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2000)) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  xlab("Total Tweets") +
  ggtitle("Republicans") +
  theme(plot.title = element_text(size=10))

grid.newpage()
grid.draw(rbind(ggplotGrob(t.T), ggplotGrob(t.D),
                ggplotGrob(t.R), size="last"))

# LOGGED DISTRIBUTION
t.lT <- ggplot(ohppa.total, aes(x=log(total.tweets))) +
  geom_histogram(fill="purple4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Logged Total Tweets by 116th House (Jan 2019-Jan 2020)") +
  theme(plot.title = element_text(size=10))

t.lD <- ggplot(ohppa.total %>% filter(party.code==100), aes(x=log(total.tweets))) +
  geom_histogram(fill="blue4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  ggtitle("Democrats") +
  theme(plot.title = element_text(size=10))

t.lR <- ggplot(ohppa.total %>% filter(party.code==200), aes(x=log(total.tweets))) +
  geom_histogram(fill="red4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  ylim(c(0,30)) +
  ylab("") +
  xlab("Logged Total Tweets") +
  ggtitle("Republicans") +
  theme(plot.title = element_text(size=10))

grid.newpage()
grid.draw(rbind(ggplotGrob(t.lT), ggplotGrob(t.lD),
                ggplotGrob(t.lR), size="last"))

ohppa.total %>% arrange(desc(total.tweets)) %>% select(name, state.abb, district, party.code, total.tweets)
```
RESTRICT TO JAN-NOV 2019
```{r}
ohppa.D.jn <- official.house.prepandemic.tweet.count %>%
  filter(party.code==100 & date <= as.Date("2019-11-28")) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohppa.R.jn <- official.house.prepandemic.tweet.count %>%
  filter(party.code==200 & date <= as.Date("2019-11-28")) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohppa.total.jn <- official.house.prepandemic.tweet.count[,1:14] %>%
  filter(date <= as.Date("2019-11-28")) %>%
  group_by(name) %>% 
  mutate(total.tweets=sum(num.tweets)) %>%
  select(-date,-num.tweets) %>% 
  distinct()
```

```{r}
# RAW DISTRIBUTION
t.T.jn <- ggplot(ohppa.total.jn, aes(x=total.tweets)) +
  geom_histogram(fill="purple4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2500)) +
  ylim(c(0,50)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Total Tweets for 116th House (Jan 2019-Jan 2020)") +
  theme(plot.title = element_text(size=10))

t.D.jn <- ggplot(ohppa.total.jn %>% filter(party.code==100), aes(x=total.tweets)) +
  geom_histogram(fill="blue4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2500)) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  ggtitle("Democrats") +
  theme(plot.title = element_text(size=10))

t.R.jn <- ggplot(ohppa.total.jn %>% filter(party.code==200), aes(x=total.tweets)) +
  geom_histogram(fill="red4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,2500)) +
  ylim(c(0,30)) +
  xlab("") +
  ylab("") +
  xlab("Total Tweets") +
  ggtitle("Republicans") +
  theme(plot.title = element_text(size=10))

grid.newpage()
grid.draw(rbind(ggplotGrob(t.T.jn), ggplotGrob(t.D.jn),
                ggplotGrob(t.R.jn), size="last"))

# LOGGED DISTRIBUTION
t.lT.jn <- ggplot(ohppa.total.jn, aes(x=log(total.tweets))) +
  geom_histogram(fill="purple4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Logged Total Tweets by 116th House (Jan 2019-Jan 2020)") +
  theme(plot.title = element_text(size=10))

t.lD.jn <- ggplot(ohppa.total.jn %>% filter(party.code==100), aes(x=log(total.tweets))) +
  geom_histogram(fill="blue4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  ylim(c(0,40)) +
  xlab("") +
  ylab("") +
  ggtitle("Democrats") +
  theme(plot.title = element_text(size=10))

t.lR.jn <- ggplot(ohppa.total.jn %>% filter(party.code==200), aes(x=log(total.tweets))) +
  geom_histogram(fill="red4", color="gray15", bins=50) +
  theme_bw() +
  scale_x_continuous(labels = scales::comma,
                     limits=c(0,10)) +
  ylim(c(0,40)) +
  ylab("") +
  xlab("Logged Total Tweets") +
  ggtitle("Republicans") +
  theme(plot.title = element_text(size=10))

grid.newpage()
grid.draw(rbind(ggplotGrob(t.lT.jn), ggplotGrob(t.lD.jn),
                ggplotGrob(t.lR.jn), size="last"))

ohppa.total.jn %>% arrange(desc(total.tweets)) %>% select(name, state.abb, district, party.code, total.tweets)
```
COMPARING PREPANDEMIC AND PANDEMIC TWEET DATA

PREP THE DATA
```{r}
official.house.prepost <- bind_rows(official.house.prepandemic.tweet.count, 
                                    official.house.pandemic.tweet.count[,1:16])

official.house.prepost$date <- as.Date(official.house.prepost$date)

ohpall.D <- official.house.prepost %>%
  filter(party.code==100) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohpall.R <- official.house.prepost %>%
  filter(party.code==200) %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)

ohpall.total <- official.house.prepost %>% 
  group_by(date) %>% 
  summarize(num.tweets=sum(num.tweets)) %>%
  left_join(covid.national)
```

UNIFIED TIME SERIES
```{r}
s1 <- ggplot(ohpall.total, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="purple4") +
  geom_vline(xintercept=as.Date("2020-01-20"), 
             linetype="dashed", 
             color="orangered2") +
  ylab("Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 9,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("116th House Tweet Frequency (Jan 2019-Nov 2020)")


s2 <- ggplot(ohpall.D, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="darkblue") +
  geom_vline(xintercept=as.Date("2020-01-20"), 
             linetype="dashed", 
             color="orangered2") +
  ylab("Democrat Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

s3 <- ggplot(ohpall.R, aes(x=date)) +
  geom_line(aes(y=num.tweets), size=0.5, color="darkred") +
  geom_vline(xintercept=as.Date("2020-01-20"), 
             linetype="dashed", 
             color="orangered2") +
  ylab("Republican Tweets") +
  xlab("") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(angle=60,hjust=1)) +
  scale_x_date(date_breaks="1 month", date_labels="%b") +
grid.newpage()
grid.draw(rbind(ggplotGrob(s1), ggplotGrob(s2),
                ggplotGrob(s3), size="last"))
```
What if I apply a rolling average?
```{r}
s4 <- ggplot(ohpall.total, aes(x=date)) +
  geom_line(aes(y=rollmean(num.tweets,7, na.pad=T)), size=0.5, color="purple4") +
  geom_vline(xintercept=as.Date("2020-01-20"), 
             linetype="dashed", 
             color="orangered2") +
  ylab("Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 9,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("116th House 7 Day Rolling Average Tweet Frequency (Jan 2019-Nov 2020)")


s5 <- ggplot(ohpall.D, aes(x=date)) +
  geom_line(aes(y=rollmean(num.tweets,7, na.pad=T)), size=0.5, color="darkblue") +
  geom_vline(xintercept=as.Date("2020-01-20"), 
             linetype="dashed", 
             color="orangered2") +
  ylab("Democrat Tweets") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ylim(c(0,800))

s6 <- ggplot(ohpall.R, aes(x=date)) +
  geom_line(aes(y=rollmean(num.tweets,7, na.pad=T)), size=0.5, color="darkred") +
  geom_vline(xintercept=as.Date("2020-01-20"), 
             linetype="dashed", 
             color="orangered2") +
  ylab("Republican Tweets") +
  xlab("") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_text(size = 7,
                                    margin = margin(r = 10)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(angle=60,hjust=1)) +
  scale_x_date(date_breaks="1 month", date_labels="%b") +
  ylim(c(0,800))

grid.newpage()
grid.draw(rbind(ggplotGrob(s4), ggplotGrob(s5),
                ggplotGrob(s6), size="last"))
```
Comparing Prepandemic to Pandemic
```{r}
prepost.compare <- official.house.prepost %>%
  mutate(pandemic = case_when(
    date >= as.Date("2019-01-20") & date <= as.Date("2019-11-28") ~ 0,
    date >= as.Date("2020-01-20") & date <= as.Date("2020-11-28") ~ 1
  )) %>% 
  group_by(name, pandemic) %>% 
  summarize(num.tweets=sum(num.tweets),
            pandemic=pandemic,
            party.code=party.code,
            year.born=year.born,
            dwnom.dim1=dwnom.dim1,
            dwnom.dim2=dwnom.dim2,
            career.start=career.start,
            chamber=chamber) %>%
  drop_na %>% 
  distinct()
```

Comparing Distributions
```{r}
ggplot(prepost.compare, aes(x=num.tweets, fill=as.factor(pandemic))) +
  geom_density(alpha=0.65) +
  scale_fill_manual(values=c("darkgreen","darkorange"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Total Member Tweets") +
  ylab("Density") +
  ggtitle("116th House Tweet Frequency Distribution") +
  xlim(c(0,2500))

ggplot(prepost.compare %>% filter(party.code==100), aes(x=num.tweets, fill=as.factor(pandemic))) +
  geom_density(alpha=0.65) +
  scale_fill_manual(values=c("blue","cyan"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Total Member Tweets") +
  ylab("Density") +
  ggtitle("116th House Democrat Tweet Frequency Distribution") +
  xlim(c(0,2500))

ggplot(prepost.compare %>% filter(party.code==200), aes(x=num.tweets, fill=as.factor(pandemic))) +
  geom_density(alpha=0.65) +
  scale_fill_manual(values=c("hotpink4","coral2"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Total Member Tweets") +
  ylab("Density") +
  ggtitle("116th House Republican Tweet Frequency Distribution") +
  xlim(c(0,2500))
```

Comparing Summary Statistics
```{r}
print("Prepandemic All:")
summary((prepost.compare %>% filter(pandemic==0))$num.tweets)
print("")
       
print("Pandemic All:")
summary((prepost.compare %>% filter(pandemic==1))$num.tweets)
print("")

print("Prepandemic Democrats:")
summary((prepost.compare %>% filter(pandemic==0, party.code==100))$num.tweets)
print("")
       
print("Pandemic Democrats:")
summary((prepost.compare %>% filter(pandemic==1, party.code==100))$num.tweets)
print("")

print("Prepandemic Republicans:")
summary((prepost.compare %>% filter(pandemic==0, party.code==200))$num.tweets)
print("")
       
print("Pandemic Republicans:")
summary((prepost.compare %>% filter(pandemic==1, party.code==200))$num.tweets)
print("")
```
BOXPLOTS PREPOST
```{r}
ggplot(prepost.compare, aes(as.factor(pandemic), num.tweets)) +
  geom_boxplot(color="purple4") +
  theme_bw() +
  xlab("Pandemic Treatment") +
  ylab("Number of Tweets") +
  ggtitle("House")

ggplot(prepost.compare %>% filter(party.code==100), aes(as.factor(pandemic), num.tweets)) +
  geom_boxplot(color="darkblue") +
  theme_bw() +
  xlab("Pandemic Treatment") +
  ylab("Number of Tweets") +
  ggtitle("House Democrats")

ggplot(prepost.compare %>% filter(party.code==200), aes(as.factor(pandemic), num.tweets)) +
  geom_boxplot(color="darkred") +
  theme_bw() +
  xlab("Pandemic Treatment") +
  ylab("Number of Tweets") +
  ggtitle("House Republicans")

#t.test(num.tweets~as.factor(pandemic),data=prepost.compare,paired=T)
```
PREPANDEMIC REGRESSIONS
```{r}
ohppa.total.jn <- ohppa.total.jn %>% filter(party.code!=328) %>% mutate(party = recode(party.code, `100`=1, `200`=0))

tweets_on_years_pre <- lm(total.tweets ~ year.born, data=ohppa.total.jn)
tweets_on_years_res_pre <-resid(tweets_on_years)
tweets_on_party_pre <- lm(total.tweets ~ party, data=ohppa.total.jn)
tweets_on_years_party_pre <- lm(total.tweets ~ year.born + party, data=ohppa.total.jn)
tweets_on_years_party_int_pre <- lm(total.tweets ~ year.born*party, data=ohppa.total.jn)
summary(tweets_on_years_party_int_pre)

ms3 <- modelsummary(list(tweets_on_years_pre, tweets_on_party_pre, tweets_on_years_party_pre, tweets_on_years_party_int_pre), 
             stars=T,
             output="kableExtra")

save_kable(ms3, "Tables/tweets_on_age_party_pre.png")


# Testing party and dwnom dim1
tweets_on_dim1_pre <- lm(total.tweets ~ dwnom.dim1, data=ohppa.total.jn)
tweets_on_years_dim1_pre <- lm(total.tweets ~ year.born + dwnom.dim1, data=ohppa.total.jn)
tweets_on_years_dim1_int_pre <- lm(total.tweets ~ year.born*dwnom.dim1, data=ohppa.total.jn)
summary(tweets_on_years_dim1_int_pre)

ms4 <- modelsummary(list(tweets_on_years_pre, tweets_on_dim1_pre, tweets_on_years_dim1_pre, tweets_on_years_dim1_int_pre), 
             stars=T,
             output="kableExtra")

save_kable(ms4, "Tables/tweets_on_age_dim1_pre.png")


prepost.compare <- prepost.compare %>% filter(party.code!=328) %>% mutate(party = recode(party.code, `100`=1, `200`=0))

ggplot(prepost.compare, aes(x=year.born, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Tweet Frequency and Year Born") +
  xlab("Year Born") +
  ylab("Total Number of Member Tweets")

ggplot(prepost.compare, aes(x=party, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Tweet Frequency and Party") +
  xlab("party") +
  ylab("Total Number of Member Tweets")

ggplot(prepost.compare %>% filter(party==0), aes(x=year.born, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Democrat Tweet Frequency and Year Born") +
  xlab("Year Born") +
  ylab("Total Number of Member Tweets")

ggplot(prepost.compare %>% filter(party==1), aes(x=year.born, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Republican Tweet Frequency and Year Born") +
  xlab("Year Born") +
  ylab("Total Number of Member Tweets")


#DW NOM

ggplot(prepost.compare, aes(x=dwnom.dim1, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Tweet Frequency and Ideology") +
  xlab("DW-NOMINATE Score") +
  ylab("Total Number of Member Tweets")

ggplot(prepost.compare, aes(x=abs(dwnom.dim1), y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Tweet Frequency and Ideological Extremity") +
  xlab("|DW-NOMINATE|") +
  ylab("Total Number of Member Tweets")

ggplot(prepost.compare %>% filter(party.code==100), aes(x=dwnom.dim1, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Democrat Tweet Frequency and Ideology") +
  xlab("DW-NOMINATE Score") +
  ylab("Total Number of Member Tweets")

ggplot(prepost.compare %>% filter(party.code==200), aes(x=dwnom.dim1, y=num.tweets, color=as.factor(pandemic))) +
  geom_point(size=0.75) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("darkgreen","chocolate3"), name="", labels=c("Prepandemic (Jan-Nov 2019)", "Pandemic (Jan-Nov 2020)")) +
  theme_bw() +
  ggtitle("House Republican Tweet Frequency and Ideology") +
  xlab("DW-NOMINATE Score") +
  ylab("Total Number of Member Tweets")


```

